---
title: _Analysis_
subtitle: _Analysis 2_
author: hi
date: 2 Nov 2019
output: 
  html_document:
    code_folding: show
    df_print: paged
    toc: TRUE
    toc_float:
       smooth_scroll: TRUE
       collapsed: TRUE
---
<style type="text/css">
h1.title { font-size: 38px; text-align: center; }
h3.subtitle{ font-size: 26px; text-align: center; }
h4.author{ font-size: 20px; text-align: right; }
h4.date{ font-size: 16px; text-align: right; }
h1 { font-size: 32px; }
h2 { font-size: 24px; }
body{ font-size: 16px; text-align: justify}
td { font-size: 14px; }
pre { font-size: 14px;}
img[alt = Personal_Picture] { width: 200px; }
img[alt = Pet_Picture] { width: 200px; }
#TOC { color: Purple; font-size: 12px; text-align: justify; border-color: Purple; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE}
setwd("/Users/.../")
```

```{r message = FALSE}
# load the required packages
library(readxl)
library(data.table)
library(knitr)
library(matrixStats)
library(CVXR)
```

# 0
```{r}
Table_0 <- read_xlsx("data.xlsx")
Table_0 <- data.table(Table_0)
```

# 1 (Result shown in percentage %)
```{r, results='asis'}
n <- nrow(Table_0)
# Calculate the simple return for Stocks
stock_s_return <- ((Table_0[-1, "Stocks"] - Table_0[1:(n-1), "Stocks"])/Table_0[1:(n-1), "Stocks"])*100
# Calculate the simple return for Bonds
bonds_s_return <- ((Table_0[-1, "Bonds"] - Table_0[1:(n-1), "Bonds"])/Table_0[1:(n-1), "Bonds"])*100
# Calculate the simple return for MM
mm_s_return <- ((Table_0[-1, "MM"] - Table_0[1:(n-1), "MM"])/Table_0[1:(n-1), "MM"])*100
# Combind all the data
simple_return_table <- cbind(stock_s_return, bonds_s_return, mm_s_return)
simple_return_table <- cbind((Table_0[-1,"Year"]),round(simple_return_table, 2))
# show the result in a table
kable(simple_return_table, caption = "Simple return in %")
# update the simple_return_table with the original one without rounding for improving the accuracy later
simple_return_table <- cbind((Table_0[-1,"Year"]),stock_s_return, bonds_s_return, mm_s_return)
```

# 2 (Result shown in Value)
```{r, results='asis'}
# Calculate the mean
mu <- apply(simple_return_table[,2:ncol(simple_return_table)], 2, mean)
mu <- t(data.table(mu/100))
rownames(mu) <- "Sample mean μˆ"
colnames(mu) <- colnames(simple_return_table[,2:ncol(simple_return_table)])
# show the result in a table
kable(mu, caption = " Sample Mean")
```

# 3 (Result shown in Value)
```{r, results='asis'}
# Calculate the cov matrix
cov_matrix <- cov(simple_return_table[,2:ncol(simple_return_table)]/100)
# show the result in a table
kable(cov_matrix, caption = "Covariance Matrix")
```

# 4 (Result shown in Value)
```{r, results='asis'}
# calculate the geo mean for each asset
stock_g_mean <- ((product(as.matrix((1 + simple_return_table[,"Stocks"]/100))))^(1/nrow(simple_return_table))  - 1)
bond_g_mean <- ((product(as.matrix((1 + simple_return_table[,"Bonds"]/100))))^(1/nrow(simple_return_table))  - 1)
mm_g_mean <- ((product(as.matrix((1 + simple_return_table[,"MM"]/100))))^(1/nrow(simple_return_table))  - 1)
# cbind all the result
geo_mean_table <- t(data.table(c(stock_g_mean,bond_g_mean,mm_g_mean)))
rownames(geo_mean_table) <- "Sample geometric mean νˆ"
colnames(geo_mean_table) <- colnames(simple_return_table[,2:ncol(simple_return_table)])
# show the result in a table
kable(geo_mean_table, caption = "Sample geometric mean νˆ")
```

# 5
```{r}
# define the function
MVO_Min_Var <- function(mu, Sigma, beta) {
  w <- Variable(nrow(Sigma))
  # Define the problem
  prob <- Problem(Minimize(quad_form(w, Sigma)), 
                   constraints = list(sum(w) == 1, w >= 0, sum(w*mu) >= beta)) # Defind the constraints
  result <- solve(prob)
  w <- as.vector(result$getValue(w))
  names(w) <- colnames(Sigma)
  return(w)
}
```

# 6 (Result shown in Value)
```{r}
# All the beta require
beta_list <- seq(0.065, 0.105, by = 0.01)
# defind a variable
Table_4 <- data.table()
Table_4 <- sapply(beta_list, function(b) {
  # calculate the weight
  weight <- MVO_Min_Var(as.numeric(geo_mean_table), cov_matrix, b)
  # calculate the portfolio variance
  p_var <- weight %*% cov_matrix %*% weight
  # cbind the data
  Table_4_row <- c(p_var, weight)})
Table_4 <- t(Table_4)
colnames(Table_4)[1] <- "Variance"
Table_4 <- cbind(beta_list, Table_4)
colnames(Table_4)[1] <- "Rate of return β"
# show the result in a table
kable(Table_4, caption = "Table 4")
```


# 7 (Result shown in Value) (Problem requires us to mininize sharpe ratio)

$$ \min_\textbf{w} \dfrac{\textbf{w}^T \hat{\mu}}{\sqrt{\textbf{w}^T \hat{\Sigma} \textbf{w}}}  $$
$$ \implies \max_\textbf{w} \dfrac{-\textbf{w}^T \hat{\mu}}{\sqrt{\textbf{w}^T \hat{\Sigma} \textbf{w}}}  $$
It reformulates the original concave-convex FP problem

$$ f(\textbf{w}) = {-\textbf{w}^T \hat{\mu}}, g(\textbf{w}) ={\sqrt{\textbf{w}^T \hat{\Sigma} \textbf{w}}} $$

$$ f(\textbf{w}) \ is \ concave \text{, we can treat as, and }\ g(\textbf{w}) \ is \ convex  $$
as the problem 

$$ f(\textbf{w})−yg(\textbf{w}), \text{where y is a new auxiliary variable} $$

Then, we are maximizing the function
$$  \max_\textbf{w} {-\textbf{w}^T \hat{\mu}} -y{\sqrt{\textbf{w}^T \hat{\Sigma} \textbf{w}}}  $$
with constraints stated in the question. 
It is equivalent to 

$$  \min_\textbf{w} {\textbf{w}^T \hat{\mu}} + y{\sqrt{\textbf{w}^T \hat{\Sigma} \textbf{w}}}  , \ convex \ function $$
$$ \text{y is iteratively updated by} \ y^{(k)} = \dfrac{\textbf{w}^{(k)T} \hat{\mu}}{\sqrt{\textbf{w}^{(k)T} \hat{\Sigma} \textbf{w}^{(k)}}} \text{ here, until convergence}$$
with the contraints stated in the question
$$ 1^T\textbf{w} = 1, ||\textbf{w}||_1 \leq 1.5$$


```{r}
Sigma <- cov_matrix
Mu <- as.vector(mu)
N <- length(Mu)

# square-root of matrix Sigma
Sigma_12 <- chol(Sigma)

# create function for MVP
SOCP_Dinkelbach <- function(y) {
  w <- Variable(nrow(Sigma))
  prob <- Problem(Minimize(t(Mu) %*% w + y*cvxr_norm(Sigma_12 %*% w, 2)),
                  constraints = list(sum(w) == 1, 
                                     cvxr_norm(w,1) <= 1.5))
  result <- solve(prob)
  return(as.vector(result$getValue(w)))
}

# initial point (has to satisfy t(w_k) %*% Mu>=0)
i_max <- which.max(Mu)
w_k <- rep(0, N)  
w_k[i_max] <- 1

# now the iterative Dinkelbach algorithm
k <- 1
while(k == 1 || max(abs(w_k - w_prev)) > 1e-6) {
  w_prev <- w_k
  y_k <- as.numeric(t(w_k) %*% Mu / sqrt(t(w_k) %*% Sigma %*% w_k))
  w_k <- SOCP_Dinkelbach(y_k)
  k <- k + 1
}
w_Dinkelbach <- t(as.data.table(w_k))
colnames(w_Dinkelbach) <- colnames(mu)
row.names(w_Dinkelbach) <- "Weight"
kable(w_Dinkelbach, caption = "Minimum Sharpe ratio optimization by using Dinkelbach method")
```

# 8 (Result shown in Value)
## (a)
```{r}
# in sample data
in_sample = Table_0[1:(1995-1960+1),]
# out sample data
out_sample = Table_0[(1995-1960+2):nrow(Table_0), ]

in_n <- nrow(in_sample)
# Calculate the in-sample simple return for Stocks
in_stock_s_return <- ((in_sample[-1, "Stocks"] - in_sample[1:(in_n-1), "Stocks"])/in_sample[1:(in_n-1), "Stocks"])
# Calculate the simple return for Bonds
in_bonds_s_return <- ((in_sample[-1, "Bonds"] - in_sample[1:(in_n-1), "Bonds"])/in_sample[1:(in_n-1), "Bonds"])
# Calculate the simple return for MM
in_mm_s_return <- ((in_sample[-1, "MM"] - in_sample[1:(in_n-1), "MM"])/in_sample[1:(in_n-1), "MM"])
# Combind all the data
in_sample_return_table <- cbind((in_sample[-1, "Year"]), in_stock_s_return, in_bonds_s_return, in_mm_s_return)

# calculate the in-sample sample geo mean for each asset
in_stock_g_mean <- (product(as.matrix(1 + in_sample_return_table[,"Stocks"])))^(1/nrow(in_sample_return_table))  - 1
in_bond_g_mean <- (product(as.matrix(1 + in_sample_return_table[,"Bonds"])))^(1/nrow(in_sample_return_table))  - 1
in_mm_g_mean <- (product(as.matrix(1 + in_sample_return_table[,"MM"])))^(1/nrow(in_sample_return_table))  - 1
# cbind all the result
in_geo_mean_table <- t(data.table(c(in_stock_g_mean,in_bond_g_mean,in_mm_g_mean)))
rownames(in_geo_mean_table) <- "In-sample geometric mean νˆ"
colnames(in_geo_mean_table) <- colnames(in_sample_return_table[,2:ncol(in_sample_return_table)])
kable(in_geo_mean_table, caption = "In-sample geometric mean νˆ")
```

## (b)
```{r}
in_cov_matrix <- cov(in_sample_return_table[,2:ncol(in_sample_return_table)])
# show the result in a table
kable(in_cov_matrix, caption = "In-sample covariance Matrix")
```

## (c)
```{r}
beta_list <- seq(0.065, 0.105, by = 0.01)

out_n <- nrow(out_sample)
# Calculate the out-sample simple return for Stocks
out_stock_s_return <- ((out_sample[-1, "Stocks"] - out_sample[1:(out_n-1), "Stocks"])/out_sample[1:(out_n-1), "Stocks"])
# Calculate the simple return for Bonds
out_bonds_s_return <- ((out_sample[-1, "Bonds"] - out_sample[1:(out_n-1), "Bonds"])/out_sample[1:(out_n-1), "Bonds"])
# Calculate the simple return for MM
out_mm_s_return <- ((out_sample[-1, "MM"] - out_sample[1:(out_n-1), "MM"])/out_sample[1:(out_n-1), "MM"])
# Combind all the data
out_sample_return_table <- cbind((out_sample[-1, "Year"]), out_stock_s_return, out_bonds_s_return, out_mm_s_return)

# Calculate the out-sample matrix
out_cov_matrix <- cov(out_sample_return_table[,2:ncol(out_sample_return_table)])

# data table to combind all the data we need
Table_7 <- data.table()
Table_7 <- sapply(beta_list, function(b) {
  # Calculate the weight by using in-sample data
  weight <- MVO_Min_Var(as.numeric(in_geo_mean_table), in_cov_matrix, b)
  # Calculate the in-sample portfolio variance
  in_p_var <- weight %*% in_cov_matrix %*% weight
  # Calculate the out-sample portfolio variance
  out_p_var <- weight %*% out_cov_matrix %*% weight
  Table_4_row <- c(in_p_var, out_p_var, weight)})
Table_7 <- t(Table_7)
colnames(Table_7)[1] <- "In-sample variance"
colnames(Table_7)[2] <- "Out-sample variance"
Table_7 <- cbind(beta_list, Table_7)
colnames(Table_7)[1] <- "Rate of return β"

# show the result in a table
kable(Table_7, caption = "Table 7")
```

